### 2025-01-28 paper/icml25/first/sects/shacpp.tex
provide a anonymous reference to code repository
minor on l' (is it ok like this? @f14-bertolotti
clarify again the goal of the proposed approach in the introduction

\begin{figure*}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shac.pdf}
        \caption{SHAC}%
        \label{fig:shac}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shacpp.pdf}
        \caption{\fname{}}%
        \label{fig:shacpp}
    \end{subfigure}
    \caption{Comparison between SHAC and \fname{}. Nodes with labels (such as $r_i$ or $r'_i$ represents values). Nodes without labels (such as $\pi$ or $R$) represents functions. Dashed lines are used to represent non differentiability. $a_i$ and $r_i$ represent the collection of actions and rewards for all agents}\label{fig:shac-shacpp}
\end{figure*}

@@

$$\mathcal{L}_\theta^\pi(\batch) + \alpha \frac{1}{\bs\horizon}\sum_{\tau\in\batch}\sum_{a\in\tau} d(a^\tau,(l,r))$$
$$d(x,(l,r)) = \begin{cases}(x-l)^2 & \text{if } x < l \\ (x-r)^2 & \text{if } x > r \\ 0 & \text{otherwise} \end{cases}$$

@@

The full implementation is openly available at 
\begin{center}
\url{https://redacted/for/anonymity}
\end{center}

>>>>

\begin{figure*}[t]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shac.pdf}
        \caption{SHAC}%
        \label{fig:shac}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/shacpp.pdf}
        \caption{\fname{}}%
        \label{fig:shacpp}
    \end{subfigure}
    \caption{Comparison between SHAC and \fname{}. Nodes with labels (such as $r_i$ or $r'_i$) values. Nodes without labels (such as $\pi$ or $R$) represent functions. Dashed lines are used to represent non differentiability. $a_i$ and $r_i$ represent the collection of actions and rewards for all agents}\label{fig:shac-shacpp}
\end{figure*}

@@

$$\mathcal{L'}_\theta^\pi(B) = \mathcal{L}_\theta^\pi(\batch) + \alpha \frac{1}{\bs\horizon}\sum_{\tau\in\batch}\sum_{a\in\tau} d(a^\tau,(l,r))$$
$$d(x,(l,r)) = \begin{cases}(x-l)^2 & \text{if } x < l \\ (x-r)^2 & \text{if } x > r \\ 0 & \text{otherwise} \end{cases}$$

@@

The full implementation is openly available at \url{https://anonymous.4open.science/r/diffagents-8653}\footnote{The link of the original repository will be provided upon acceptance.}.
